\singlespacing{\textbf{Efficient Pollution Abatement in Electricity Markets with Intermittent Renewable Energy}}\thanks{We would like to thank Prof. Roger Klein for helpful comments and the Sun Grant (award number 122682) for funding this project.}

### 2019-06-19 documents/draft.tex
Update draft
- draft now correctly references new figures' location

% images
\graphicspath{ {D:/Users/saketh/Documents/GitHub/BECCS-Case-Study/documents/exhibits/} }

@@

@@

@@

\begin{table}[t] \centering 
	\caption{OLS Regression Results}
	\label{table:1} 
	\small
	\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
		\\[-4ex]\hline  
		\hline \\[-1.8ex] 
		& \multicolumn{6}{c}{\textit{Dependent variable:} $\ln (Z_{ t, i} / Z_{ s, i})$} \\ [0.5ex]
		\cline{2-7} 
		\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ [0.5ex]
		\hline \\[-1.8ex] 
		$-\ln (P_{t,i} / P_{s,i})$ & 0.937$^{***}$ & 1.075$^{***}$ & 1.098$^{***}$ & 1.074$^{***}$ & 1.263$^{***}$ & 1.305$^{***}$ \\ 
		& (0.030) & (0.026) & (0.026) & (0.224) & (0.172) & (0.169) \\ 
		& & & & & & \\ 
		$\Delta_{t,s}$ &  &  & 0.0005$^{***}$ &  &  & 0.0065$^{*}$ \\ 
		&  &  & (0.0001) &  &  & (0.0003) \\ 
		& & & & & & \\ 
		CDD$_t$ &  & 1.156$^{***}$ & 1.163$^{***}$ &  & 1.164$^{***}$ & 1.174$^{***}$ \\

@@

Based on the OLS results reported in \hyperref[table:1]{Table 1}, we estimate the intertemporal elasticity of substitution for electricity consumption $\hat{\sigma}  = 1.305$ ($|t| > 24$) when accounting for all degree day covariates and state fixed effects. Additionally, we find that accounting for cooling and heating degree days captures a large amount of variation in demand for electricity; in the fixed effects regressions, adding these controls raises adjusted $R^2$ from 8.5\% to 51.8\%. Also, as expected, the coefficients on the degree day covariates are symmetrical; that is, the coefficient on $CDD_{t}$ is approximately the same as the negative of that on $CDD_{s}$, and the same applies to $HDD_{t}$ and $HDD_{s}$. \footnote{It is important to note that the reason they are not perfectly equal is because our regression data consists of each unique \textit{combination} of $(t,s)$ for each $i$; that is, if we have an arbitrary observation $(t,s,i)$ in our data, then $(s,t,i)$ does not also appear. Including these observations would not affect $\sigma$ and they also don't add any further information to our regression. However, they would make the magnitude of the estimated coefficients for  CDD$_t$ and CDD$_s$ equivalent (and likewise for HDDs). }  Furthermore, we found that electricity consumption seems to rise more in response to CDDs rather than HDDs.  Next, we find that the sign on $\Delta_{t,s}$ is positive in all regressions, so electricity consumption rises over time independent of price. Specifically, fit (6) finds a coefficient of $0.000655$ which implies that electricity consumption rises, on average, by $\approx 0.7\%$ per year. Finally, adding state fixed effects seems to raise the estimates of $\sigma$ for all fits.

To account for endogeneity in the OLS results, we provide results for our IV specification in \hyperref[table:2]{Table 2}. Here, we find a much larger estimate of $\hat{\sigma}  = 5.818$ ($|t| > 11.1$) when considering all covariates and fixed effects. F-Statistics on all three specifications are significantly larger than 10, which suggests that the instruments are not weak \citep{SS1997}. These results greatly differ from the literature's estimates probably as a consequence of controlling for endogeneity. That is, ignoring variation on the supply side would bias OLS estimates for the effect of price on demand downwards; by controlling for this, we find larger estimates of $\sigma$ which is expected. Next, with respect to the demand controls, we find results similar to those of OLS. The magnitudes of the coefficients on DDs do not appear to be significantly different. Furthermore, we again find that CDDs affect electricity consumption more than HDDs. But, this time, the coefficients on heating degree days do not appear to be significant. Additionally, in contrast with the OLS results, we find a much larger estimate for the coefficient on $\Delta_{t,s}$ of $0.003$; this implies that electricity consumption seems to rise by about 3.65\% per year. So, overall, our IV results suggest much higher estimates of $\sigma$.

Finally, we control for nonlinear effects using a partially linear IV regression reported in \hyperref[table:3]{Table 3}. Here, we find much smaller results than 2SLS when controlling for all possible covariates. Specifically, in fit (3), we have $\hat{\sigma} = 0.8847$ ($|t| > 20$). The estimates of $\sigma$ with fewer controls are much larger. However, based on the OLS and IV results, it seems that both the time control and degree day controls are significant. Hence, fit (3) is likely the most appropriate specification. Additionally, all of these estimates are significantly different from the 2SLS results which suggests that the 2SLS results are not robust. To be precise, our controls and instrument likely have non-linear effects on price and quantity which cannot be captured by linear models; this may explain why the 2SLS results differ significantly from these semiparametric results. Alternatively, this difference may also be because the errors in our regressions are not Gaussian. In any case, we  believe that our third semiparametric fit, $\hat{\sigma} = 0.8847$, is the most robust estimate of $\sigma$. We now discuss what this means for renewable energy policy in greater detail.

\begin{table}[h] \centering 
	\vspace{-2em}
	\caption{IV (2SLS) Regression Results}
	\label{table:2} 
	\small
	\begin{tabular}{@{\extracolsep{4pt}}lcccccc} 
		\\[-4ex]\hline  
		\hline \\[-1.6ex] 
		& \multicolumn{3}{c}{First-Stage} & \multicolumn{3}{c}{Second-Stage} \\ [0.5ex]
		& \multicolumn{3}{c}{\textit{Dep. Variable:} $\ln (P_{t,i} / P_{s,i})$ } & \multicolumn{3}{c}{\textit{Dep. Variable:}  $\ln (Z_{ t, i} / Z_{ s, i})$}\\ [0.5ex]
		\cmidrule(lr){2-4} \cmidrule(lr){5-7}\\[-2.2ex] 
		& (A.1) & (B.1) & (C.1) & (A.2) & (B.2) & (C.2)\\ [0.5ex]
		\hline \\[-1.8ex] 
		$ \ln (C_{t,i} / C_{s,i})$ & $-$0.042$^{***}$ & $-$0.018$^{***}$ & $-$0.018$^{***}$ &  &  &  \\ 
		& (0.002) & (0.002) & (0.002) &  &  &  \\ 
		& & & & & & \\ 
		$-\ln (P_{t,i} / P_{s,i})$ &  &  &  & 2.978$^{***}$ & 5.896$^{***}$ & 5.818$^{***}$ \\ 
		&  &  &  & (0.180) & (0.548) & (0.524) \\ 
		& & & & & & \\ 
		$\Delta_{t,s}$  &  &  & 0.001$^{***}$ &  &  & 0.003$^{***}$ \\ 
		&  &  & (0.00004) &  &  & (0.0004) \\ 
		& & & & & & \\ 
		CDD$_t$  &  & 0.100$^{***}$ & 0.105$^{***}$ &  & 1.637$^{***}$ & 1.657$^{***}$ \\ 
		$\quad(\times 1000^{-1})$ &  & (0.006) & (0.006) &  & (0.068) & (0.067) \\ 
		& & & & & & \\ 
		CDD$_s$ &  & $-$0.096$^{***}$ & $-$0.114$^{***}$ &  & $-$1.688$^{***}$ & $-$1.783$^{***}$ \\ 
		$\quad(\times 1000^{-1})$  &  & (0.009) & (0.009) &  & (0.079) & (0.084) \\ 
		& & & & & & \\ 
		HDD$_t$  &  & $-$0.048$^{***}$ & $-$0.048$^{***}$ &  & 0.001 & 0.007 \\ 
		$\quad(\times 1000^{-1})$ &  & (0.003) & (0.003) &  & (0.031) & (0.030) \\ 
		& & & & & & \\ 
		HDD$_s$  &  & 0.053$^{***}$ & 0.055$^{***}$ &  & 0.0001 & 0.007 \\ 
		$\quad(\times 1000^{-1})$  &  & (0.003) & (0.003) &  & (0.035) & (0.034) \\   [0.9ex]
		\hline \\[-1.8ex] 
		State FEs &  Yes & Yes  & Yes  & Yes & Yes & Yes \\ 
		Observations & 6817 & 6817 & 6817 & 6817 & 6817 & 6817 \\ 
		R$^{2}$ & 0.061 & 0.264 & 0.294 &  &  & \\ 
		Adjusted R$^{2}$ & 0.061 & 0.264 & 0.293 & &  &  \\ 
		F Statistic & 443$^{***}$  & 489$^{***}$ & 472$^{***}$  &  &  &  \\ 
		\hline 
		\hline \\[-1.8ex] 
		\multicolumn{7}{@{}p{41.5em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions. The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$. The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state. The coefficient on $\ln (P_{t,i} / P_{s,i})$ is an estimate of $-\sigma$. The variable $\Delta_{t,s}$ is the difference in months between periods $t$ and $s$. CDD$_t$ and HDD$_t$ refer to the total number of heating and cooling degree days in month $t$. We scale the coefficients on degree days for clarity. Robust standard errors are reported in parentheses. *p$\textless$0.05, **p$\textless$0.01, ***p$\textless$0.001}  \\ 
	\end{tabular} 
	%\end{table}
	\\[4ex]

	%\begin{table}[!t] \centering 
	\caption{Partially Linear IV Regression Results}
	\label{table:3} 
	\small
	\begin{tabular}{@{\extracolsep{5.3em}}lccc} 
		\\[-4ex]\hline  
		\hline \\[-1.8ex] 
		& \multicolumn{3}{c}{\textit{Instrument: $ \ln (C_{t,i} / C_{s,i})$}} \\ 
		\cline{2-4} 
		%\\[-1.8ex] & ln\_load\_rel \textasciitilde ln\_price\_rel & ln\_load\_rel \textasciitilde (CDD\_1) & ln\_load\_rel \textasciitilde time\_diff + (CDD\_1) \\ 
		\\[-1.8ex] & (1) & (2) & (3)\\ [0.5ex]
		\hline \\[-1.8ex] 
		$\hat{\sigma} $ & 2.9976$^{***}$ & 1.2123$^{***}$ & 0.8847$^{***}$ \\ 
		& (0.169) & (0.052) & (0.044) \\ [0.9ex]
		\hline \\[-1.8ex] 
		Time Control &   &   & Yes  \\ 
		Degree Day Controls &   & Yes  & Yes  \\ 
		Observations & 6817 & 6817 & 6817 \\
		\hline 
		\hline \\[-1.8ex] 
		\multicolumn{4}{@{}p{41.5em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions. The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$. The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state. The estimation procedure is described in the appendix.  Robust standard errors are reported in parentheses. *p$\textless$0.05, **p$\textless$0.01, ***p$\textless$0.001}  \\ 
	\end{tabular} 
\end{table}

@@

\begin{table}[t]
	\caption*{\textbf{Figure 1:} The Elasticity of Substition between Solar and Coal} 
	\label{fig:eosnum}
	\footnotesize
	\vspace{-1em}
	\begin{tabular}{@{\extracolsep{0em}}c}
		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_elasticity} \\
		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } Technology 1 is coal and technology 2 is solar. The legend in the upper subplot also applies to the lower subplot. These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$. Furthermore, we set the parameter for the intertemporal elasticity of substitution for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$. In order to generate these numerical results, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 2 \,c_1)$. Then, we obtained estimates of the elasticity of substitution by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1/ c_2)$. That is, the elasticity of substitution  between technology 1 and 2 is given by the slope of the upper subplot, and it is graphed in the lower subplot. Finally, we repeat this procedure with $\sigma$ equal to two standard deviations above and below its estimated value $\hat{\sigma}$; that is, the dashed lines represent  $\sigma = 0.8847 \pm (1.96)(0.044)$. }     \\  
	\end{tabular}
\end{table}

We plot our numerical estimates of $e_{1, 2}$, the elasticity of substitution between solar and coal power, in \hyperref[fig:eosnum]{Figure 1}. We generated these results by computing the optimal quantities of each technology given a range of relative prices $c_2/c_1$. Then, we numerically differentiated $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$ to estimate the elasticity of substitution between solar and coal. This numerically computed elasticity of substitution between solar and coal power, $e_{solar,coal}$, is shown in the lower subplot. We repeat this process with different values of $\sigma$, the elasticity of substitution in the consumer's utility function. Specifically, we use our estimate of $\hat{\sigma} = 0.8847\, (0.044)$ and its 95\%  confidence interval $(0.7985, 0.9709)$.  Finally, after finding the optimal values of our quantities $X$, we filter all observations of our numerical simulation that correspond to edge cases -- solutions where $X, Z \leq  0$.

The first relationship we see in \hyperref[fig:eosnum]{Figure 1} is that $e_{1,2}$ varies non-linearly with the relative costs of each technology; in particular, it appears to take on a hockey stick shape. This shape is a result of both intermittency and costs. Intermittency reduces substitutability as overall energy generation becomes more intermittent. In other words, intermittency is a bigger issue for consumers when their energy supply is not consistent. This causes $e_{1,2}$ to fall when the majority of energy generated comes from solar; naturally, the latter occurs when $\log(c_2/c_1)$ is small (solar is relatively cheap). At the same time, quantities become more sensitive to costs when costs greatly differ.\footnote{We explore this point further in Appendix B in which we consider a numerical example where technologies are minimally intermittent. That is, we again consider a two-period, two-technology example, but assume that $\xi_1$ and $\xi_2$ are nearly constant over time. We plot our results in \hyperref[fig:eosrange]{Figure B.1} and find that the elasticity of substitution takes on a u-shape. } That is, $e_{1,2}$ rises when the relative prices of solar and coal are very different. When these two effects interact, we see the elasticity of substitution between solar and coal takes on a hockey stick shape.

% Middle of paragraph (hard to understand?)
% To understand why, let us consider three cases. For the first case, suppose coal is relatively far cheaper than solar ($\log(c_2/c_1)$ is large). This suggests producers will primarily employ coal for electricity. Because the output of coal does not vary with time, we will have a constant amount of electricity through the day. Consequently, the intermittency will not matter much on the margin since generation is already quite consistent. Instead, the cost of a competing generation technology will play a much bigger role. Consequently, solar and coal will be strong substitutes; this explains why $e_{1,2}$ is much larger when $\log(c_2/c_1)$ is large. On the other hand, for the second case, suppose that the price of solar and coal are such that we use about an equal amount of both. This corresponds to the point where $\log(c_2/c_1)  = -0.7$ in the \hyperref[fig:eosnum]{Figure 1}. In this case, output will not be constant through the day, since a large portion of electricity is coming from solar. As a result, consumers will care about intermittency on the margin; so, the  intermittency effect will matters in this case and will impede the adoption of solar. As a result, coal and solar will be relatively weaker substitutes; thus, we see $e_{1,2}$ is relatively lower when relative prices are not at extrema. Finally, consider the third case where solar is relatively much cheaper than coal. In this case, the quantity of solar is much larger than that of coal; this causes overall electricity output to be very intermittent. So, again, the intermittency effect matters. However, since the cost of each technology differs greatly, small changes in price could cause large changes in quantity. Accounting for both these factors, we see a moderately large elasticity of substitution $e_{1,2}$ when $\log(c_2/c_1)$ is small.

Additionally, note that the elasticity of substitution $e_{1,2}$ between solar and coal becomes larger and more non-linear as $\sigma$ rises. Firstly, the reason why  it becomes larger is fairly intuitive. When a consumer's intertemporal elasticity of substitution for electricity consumption $\sigma$ is large, they will be more sensitive to changes in the price of electricity and more willing to substitute their electricity consumption across periods. As a result, the intermittency of solar becomes less of an  issue for consumers, but its relative price with respect to coal will play a bigger role. Consequently, this implies that the elasticity of substitution $e_{1, 2}$ will be larger. Hence, in the lower subplot of \hyperref[fig:eosnum]{Figure 1}, we see that $e_{1, 2}$ rises with $\sigma$ when holding the  relative prices of each technology constant. Secondly, we find that $e_{1,2}$ becomes more u-shaped as $\sigma$ rises. This is because larger values of $\sigma$ weaken the disincentive created by intermittency. Consequently, the shape of the elasticity of substitution $e_{1,2}$ becomes more dependent on the relative costs. As argued earlier, when costs differ greatly between technologies, the elasticity of substitution $e_{1,2}$ is higher.

%Additionally, note that we assumed earlier that the estimates of $\sigma$ on a monthly basis would be fairly close to those on a daily or hourly basis. But, our results showed estimates of $\hat{\sigma} \approx 0.5$ which differs from the literatures' estimates which fall between $0.01$ and $0.25$. Does this impact our numerical results? Alternatively, if our estimates were closer to past estimates, would there be significantly different economic implications? Based on our numerical model, the answer seems to be no. That is, the relationship between $e$ and $\log(c_2/c_1)$ in \hyperref[fig:eosnum]{Figure 1} does not significantly differ when varying $\sigma$ in $\{0.05, 0.25, 0.5\}$. Hence, even if our assumption is incorrect or past estimates are biased, our model's results do not significantly differ within this range of estimates for $\sigma$.

%\footnote{ Recall that $\sigma < 1$ implies that  electricity consumption in different periods are complements, $\sigma = 1$ implies to a Cobb-Douglas relationship, and $\sigma > 1$ implies that electricity consumption in different periods are substitutes.}

@@

%\subsubsection{Technical Change and the Adoption of Renewable Energy}
% 

>>>>

% images
%\graphicspath{ {D:/Users/saketh/Documents/GitHub/Energy-Intermittency-Paper/figures/} }

@@

% caption set up
\captionsetup[figure]{
	font = {sc},
	labelfont = {bf}
}

@@

	\begin{table}[t] \centering 
		\caption{Descriptive Statistics}
		\label{table:stats} 
		\begin{tabular}{@{\extracolsep{0pt}}lrrrrrrr@{}}
			\\[-4ex]\hline  
			\hline \\[-1.8ex] 
			{} &     Mean &      StDev  &     Min &     25\% &      50\% &      75\% &       Max \\
			\midrule
			Electricity Price (\$/kWh)     &     0.12 &     0.03 &    0.08 &    0.10 &     0.11 &     0.13 &      0.21 \\
			Electricity Load (GwH) & 2454.97 &  2380.24 &  144.00 &  790.50 &  1869.50 &  3315.00 &  18621.00 \\
			Coal Price (\$/ton) &    46.00 &    17.68 &   24.04 &   33.43 &    41.40 &    51.83 &    107.49 \\
			Cooling Degree Days      &    64.66 &   134.97 &    0.00 &    0.00 &     0.00 &    47.25 &    761.00 \\
			Heating Degree Days       &   443.20 &   412.27 &    0.00 &   48.00 &   367.00 &   754.50 &   1794.00 \\ [0.5ex]
			\hline 
			\hline \\[-1.8ex] 
			\multicolumn{8}{@{}p{41.5em}@{}}{\textit{Note: } The underlying data covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable. Each observation corresponds to a particular year, month, and state. }  \\ 
		\end{tabular}
	\end{table}

@@

	\begin{table}[t] \centering 
		\caption{OLS Regression Results}
		\label{table:ols} 
		\small
		\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
			\\[-4ex]\hline  
			\hline \\[-1.8ex] 
			& \multicolumn{6}{c}{\textit{Dependent variable:} $\ln (Z_{ t, i} / Z_{ s, i})$} \\ [0.5ex]
			\cline{2-7} 
			\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ [0.5ex]
			\hline \\[-1.8ex] 
			$-\ln (P_{t,i} / P_{s,i})$ & 0.937$^{***}$ & 1.075$^{***}$ & 1.098$^{***}$ & 1.074$^{***}$ & 1.263$^{***}$ & 1.305$^{***}$ \\ 
			& (0.030) & (0.026) & (0.026) & (0.224) & (0.172) & (0.169) \\ 
			& & & & & & \\ 
			$\Delta_{t,s}$ &  &  & 0.0005$^{***}$ &  &  & 0.0065$^{*}$ \\ 
			&  &  & (0.0001) &  &  & (0.0003) \\ 
			& & & & & & \\ 
			CDD$_t$ &  & 1.156$^{***}$ & 1.163$^{***}$ &  & 1.164$^{***}$ & 1.174$^{***}$ \\

@@

	Based on the OLS results reported in \autoref{table:ols} we estimate the intertemporal elasticity of substitution for electricity consumption $\hat{\sigma}  = 1.305$ ($|t| > 24$) when accounting for all degree day covariates and state fixed effects. Additionally, we find that accounting for cooling and heating degree days captures a large amount of variation in demand for electricity; in the fixed effects regressions, adding these controls raises adjusted $R^2$ from 8.5\% to 51.8\%. Also, as expected, the coefficients on the degree day covariates are symmetrical; that is, the coefficient on $CDD_{t}$ is approximately the same as the negative of that on $CDD_{s}$, and the same applies to $HDD_{t}$ and $HDD_{s}$. \footnote{It is important to note that the reason they are not perfectly equal is because our regression data consists of each unique \textit{combination} of $(t,s)$ for each $i$; that is, if we have an arbitrary observation $(t,s,i)$ in our data, then $(s,t,i)$ does not also appear. Including these observations would not affect $\sigma$ and they also don't add any further information to our regression. However, they would make the magnitude of the estimated coefficients for  CDD$_t$ and CDD$_s$ equivalent (and likewise for HDDs). }  Furthermore, we found that electricity consumption seems to rise more in response to CDDs rather than HDDs.  Next, we find that the sign on $\Delta_{t,s}$ is positive in all regressions, so electricity consumption rises over time independent of price. Specifically, fit (6) finds a coefficient of $0.000655$ which implies that electricity consumption rises, on average, by $\approx 0.7\%$ per year. Finally, adding state fixed effects seems to raise the estimates of $\sigma$ for all fits.

	To account for endogeneity in the OLS results, we provide results for our IV specification in \autoref{table:iv}. Here, we find a much larger estimate of $\hat{\sigma}  = 5.818$ ($|t| > 11.1$) when considering all covariates and fixed effects. F-Statistics on all three specifications are significantly larger than 10, which suggests that the instruments are not weak \citep{SS1997}. These results greatly differ from the literature's estimates probably as a consequence of controlling for endogeneity. That is, ignoring variation on the supply side would bias OLS estimates for the effect of price on demand downwards; by controlling for this, we find larger estimates of $\sigma$ which is expected. Next, with respect to the demand controls, we find results similar to those of OLS. The magnitudes of the coefficients on DDs do not appear to be significantly different. Furthermore, we again find that CDDs affect electricity consumption more than HDDs. But, this time, the coefficients on heating degree days do not appear to be significant. Additionally, in contrast with the OLS results, we find a much larger estimate for the coefficient on $\Delta_{t,s}$ of $0.003$; this implies that electricity consumption seems to rise by about 3.65\% per year. So, overall, our IV results suggest much higher estimates of $\sigma$.

	Finally, we control for nonlinear effects using a partially linear IV regression reported in \autoref{table:pariv}. Here, we find much smaller results than 2SLS when controlling for all possible covariates. Specifically, in fit (3), we have $\hat{\sigma} = 0.8847$ ($|t| > 20$). The estimates of $\sigma$ with fewer controls are much larger. However, based on the OLS and IV results, it seems that both the time control and degree day controls are significant. Hence, fit (3) is likely the most appropriate specification. Additionally, all of these estimates are significantly different from the 2SLS results which suggests that the 2SLS results are not robust. To be precise, our controls and instrument likely have non-linear effects on price and quantity which cannot be captured by linear models; this may explain why the 2SLS results differ significantly from these semiparametric results. Alternatively, this difference may also be because the errors in our regressions are not Gaussian. In any case, we  believe that our third semiparametric fit, $\hat{\sigma} = 0.8847$, is the most robust estimate of $\sigma$. We now discuss what this means for renewable energy policy in greater detail.

	\begin{table}[h] 
		\centering 
		\caption{IV (2SLS) Regression Results}
		\label{table:iv} 
		\small
		\begin{tabular}{@{\extracolsep{4pt}}lcccccc} 
			\\[-4ex]\hline  
			\hline \\[-1.6ex] 
			& \multicolumn{3}{c}{First-Stage} & \multicolumn{3}{c}{Second-Stage} \\ [0.5ex]
			& \multicolumn{3}{c}{\textit{Dep. Variable:} $\ln (P_{t,i} / P_{s,i})$ } & \multicolumn{3}{c}{\textit{Dep. Variable:}  $\ln (Z_{ t, i} / Z_{ s, i})$}\\ [0.5ex]
			\cmidrule(lr){2-4} \cmidrule(lr){5-7}\\[-2.2ex] 
			& (A.1) & (B.1) & (C.1) & (A.2) & (B.2) & (C.2)\\ [0.5ex]
			\hline \\[-1.8ex] 
			$ \ln (C_{t,i} / C_{s,i})$ & $-$0.042$^{***}$ & $-$0.018$^{***}$ & $-$0.018$^{***}$ &  &  &  \\ 
			& (0.002) & (0.002) & (0.002) &  &  &  \\ 
			& & & & & & \\ 
			$-\ln (P_{t,i} / P_{s,i})$ &  &  &  & 2.978$^{***}$ & 5.896$^{***}$ & 5.818$^{***}$ \\ 
			&  &  &  & (0.180) & (0.548) & (0.524) \\ 
			& & & & & & \\ 
			$\Delta_{t,s}$  &  &  & 0.001$^{***}$ &  &  & 0.003$^{***}$ \\ 
			&  &  & (0.00004) &  &  & (0.0004) \\ 
			& & & & & & \\ 
			CDD$_t$  &  & 0.100$^{***}$ & 0.105$^{***}$ &  & 1.637$^{***}$ & 1.657$^{***}$ \\ 
			$\quad(\times 1000^{-1})$ &  & (0.006) & (0.006) &  & (0.068) & (0.067) \\ 
			& & & & & & \\ 
			CDD$_s$ &  & $-$0.096$^{***}$ & $-$0.114$^{***}$ &  & $-$1.688$^{***}$ & $-$1.783$^{***}$ \\ 
			$\quad(\times 1000^{-1})$  &  & (0.009) & (0.009) &  & (0.079) & (0.084) \\ 
			& & & & & & \\ 
			HDD$_t$  &  & $-$0.048$^{***}$ & $-$0.048$^{***}$ &  & 0.001 & 0.007 \\ 
			$\quad(\times 1000^{-1})$ &  & (0.003) & (0.003) &  & (0.031) & (0.030) \\ 
			& & & & & & \\ 
			HDD$_s$  &  & 0.053$^{***}$ & 0.055$^{***}$ &  & 0.0001 & 0.007 \\ 
			$\quad(\times 1000^{-1})$  &  & (0.003) & (0.003) &  & (0.035) & (0.034) \\   [0.9ex]
			\hline \\[-1.8ex] 
			State FEs &  Yes & Yes  & Yes  & Yes & Yes & Yes \\ 
			Observations & 6817 & 6817 & 6817 & 6817 & 6817 & 6817 \\ 
			R$^{2}$ & 0.061 & 0.264 & 0.294 &  &  & \\ 
			Adjusted R$^{2}$ & 0.061 & 0.264 & 0.293 & &  &  \\ 
			F Statistic & 443$^{***}$  & 489$^{***}$ & 472$^{***}$  &  &  &  \\ 
			\hline 
			\hline \\[-1.8ex] 
			\multicolumn{7}{@{}p{41.5em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions. The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$. The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state. The coefficient on $\ln (P_{t,i} / P_{s,i})$ is an estimate of $-\sigma$. The variable $\Delta_{t,s}$ is the difference in months between periods $t$ and $s$. CDD$_t$ and HDD$_t$ refer to the total number of heating and cooling degree days in month $t$. We scale the coefficients on degree days for clarity. Robust standard errors are reported in parentheses. *p$\textless$0.05, **p$\textless$0.01, ***p$\textless$0.001}  \\ 
		\end{tabular} 
	\end{table}

	\begin{table}[!t] 
		\centering 
		\caption{Partially Linear IV Regression Results}
		\label{table:pariv} 
		\small
		\begin{tabular}{@{\extracolsep{5.3em}}lccc} 
			\\[-4ex]\hline  
			\hline \\[-1.8ex] 
			& \multicolumn{3}{c}{\textit{Instrument: $ \ln (C_{t,i} / C_{s,i})$}} \\ 
			\cline{2-4} 
			%\\[-1.8ex] & ln\_load\_rel \textasciitilde ln\_price\_rel & ln\_load\_rel \textasciitilde (CDD\_1) & ln\_load\_rel \textasciitilde time\_diff + (CDD\_1) \\ 
			\\[-1.8ex] & (1) & (2) & (3)\\ [0.5ex]
			\hline \\[-1.8ex] 
			$\hat{\sigma} $ & 2.9976$^{***}$ & 1.2123$^{***}$ & 0.8847$^{***}$ \\ 
			& (0.169) & (0.052) & (0.044) \\ [0.9ex]
			\hline \\[-1.8ex] 
			Time Control &   &   & Yes  \\ 
			Degree Day Controls &   & Yes  & Yes  \\ 
			Observations & 6817 & 6817 & 6817 \\
			\hline 
			\hline \\[-1.8ex] 
			\multicolumn{4}{@{}p{41.5em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions. The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$. The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state. The estimation procedure is described in the appendix.  Robust standard errors are reported in parentheses. *p$\textless$0.05, **p$\textless$0.01, ***p$\textless$0.001}  \\ 
		\end{tabular} 
	\end{table}

@@

	\begin{figure}[t]
		\caption{The Elasticity of Substitution between Solar and Coal} 
		\label{fig:eosnum}
		\footnotesize
		\vspace{-1em}
		\begin{tabular}{@{\extracolsep{0em}}c}
			\includegraphics[width=1\linewidth]{../figures/fig_elasticity} \\
			\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } Technology 1 is coal and technology 2 is solar. The legend in the upper subplot also applies to the lower subplot. These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$. Furthermore, we set the parameter for the intertemporal elasticity of substitution for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$. In order to generate these numerical results, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 2 \,c_1)$. Then, we obtained estimates of the elasticity of substitution by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1/ c_2)$. That is, the elasticity of substitution  between technology 1 and 2 is given by the slope of the upper subplot, and it is graphed in the lower subplot. Finally, we repeat this procedure with $\sigma$ equal to two standard deviations above and below its estimated value $\hat{\sigma}$; that is, the dashed lines represent  $\sigma = 0.8847 \pm (1.96)(0.044)$. }     \\  
		\end{tabular}
	\end{figure}

	We plot our numerical estimates of $e_{1, 2}$, the elasticity of substitution between solar and coal power, in \autoref{fig:eosnum}. We generated these results by computing the optimal quantities of each technology given a range of relative prices $c_2/c_1$. Then, we numerically differentiated $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$ to estimate the elasticity of substitution between solar and coal. This numerically computed elasticity of substitution between solar and coal power, $e_{solar,coal}$, is shown in the lower subplot. We repeat this process with different values of $\sigma$, the elasticity of substitution in the consumer's utility function. Specifically, we use our estimate of $\hat{\sigma} = 0.8847\, (0.044)$ and its 95\%  confidence interval $(0.7985, 0.9709)$.  Finally, after finding the optimal values of our quantities $X$, we filter all observations of our numerical simulation that correspond to edge cases -- solutions where $X, Z \leq  0$.

	The first relationship we see in \autoref{fig:eosnum} is that $e_{1,2}$ varies non-linearly with the relative costs of each technology; in particular, it appears to take on a hockey stick shape. This shape is a result of both intermittency and costs. Intermittency reduces substitutability as overall energy generation becomes more intermittent. In other words, intermittency is a bigger issue for consumers when their energy supply is not consistent. This causes $e_{1,2}$ to fall when the majority of energy generated comes from solar; naturally, the latter occurs when $\log(c_2/c_1)$ is small (solar is relatively cheap). At the same time, quantities become more sensitive to costs when costs greatly differ.\footnote{We explore this point further in Appendix B in which we consider a numerical example where technologies are minimally intermittent. That is, we again consider a two-period, two-technology example, but assume that $\xi_1$ and $\xi_2$ are nearly constant over time. We plot our results in \autoref{fig:eosrange} and find that the elasticity of substitution takes on a u-shape. } That is, $e_{1,2}$ rises when the relative prices of solar and coal are very different. When these two effects interact, we see the elasticity of substitution between solar and coal takes on a hockey stick shape.

	Additionally, note that the elasticity of substitution $e_{1,2}$ between solar and coal becomes larger and more non-linear as $\sigma$ rises. Firstly, the reason why  it becomes larger is fairly intuitive. When a consumer's intertemporal elasticity of substitution for electricity consumption $\sigma$ is large, they will be more sensitive to changes in the price of electricity and more willing to substitute their electricity consumption across periods. As a result, the intermittency of solar becomes less of an  issue for consumers, but its relative price with respect to coal will play a bigger role. Consequently, this implies that the elasticity of substitution $e_{1, 2}$ will be larger. Hence, in the lower subplot of \autoref{fig:eosnum}, we see that $e_{1, 2}$ rises with $\sigma$ when holding the  relative prices of each technology constant. Secondly, we find that $e_{1,2}$ becomes more u-shaped as $\sigma$ rises. This is because larger values of $\sigma$ weaken the disincentive created by intermittency. Consequently, the shape of the elasticity of substitution $e_{1,2}$ becomes more dependent on the relative costs. As argued earlier, when costs differ greatly between technologies, the elasticity of substitution $e_{1,2}$ is higher.

@@
